Initial Analysis

### 2020-08-04 Scripts/Initial_Analysis.Rmd
Fixed matching names nightmare and created weight plots

# Requires Clean_sau_eez_fes
# Data <- Results_Trans
CleanResults <- function(Data){

  # Clean out countries that share with their own borders (e.g. Brazil mainland and Brazil (Fernando de Noronha))
  Auto_Remove_Territories <- Data %>% 
    filter(!is.na(Territory),
           !is.na(Neighbour)) %>% 
    rename(eez_name=Territory) %>% 
    left_join(Clean_sau_eez_fes,
              by = "eez_name") %>% 
    select(TaxonKey,
           Territory= eez_name,
           eez_name=Neighbour, 
           Model_Index,
           Area_Index,
           CT_fishing_entity= fishing_entity) %>% 
    left_join(Clean_sau_eez_fes,
              by = "eez_name") %>% 
    select(1,2, 
           Neighbour = eez_name,
           Model_Index:CT_fishing_entity,
           NT_fishing_entity= fishing_entity,
           everything()) %>% 
    mutate(
      CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Territory),paste(CT_fishing_entity)),
      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour),paste(NT_fishing_entity)),
      Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
    )

@@

  # Complete list of territories to remove from dataset (Including islands)
  Territories_to_Remove <- Data %>% 
    filter(
      Territory %in% Islands_to_Remove |
        Neighbour %in% Islands_to_Remove |
        Territory == "Balearic Island (Spain)" & Neighbour == "Spain (Mediterranean and Gulf of Cadiz)" |
        Territory == "British Virgin Isl. (UK)" & Neighbour == "Anguilla" |
        Neighbour == "British Virgin Isl. (UK)" & Territory == "Anguilla" |
        Territory == "Corsica (France)" & Neighbour == "France (Mediterranean)" |
        Neighbour == "Corsica (France)" & Territory == "France (Mediterranean)" |
        Territory == "Crete (Greece)" & Neighbour == "Grece" |
        Neighbour == "Crete (Greece)" & Territory == "Grece" |
        Territory == "Cyprus (North)" & Neighbour == "Cyprus (South)" |
        Neighbour == "Cyprus (North)" & Territory == "Cyprus (South)" |
        Territory == "Channel Isl. (UK)" & Neighbour == "United Kingdom" |
        Neighbour == "Channel Isl. (UK)" & Territory == "United Kingdom" |
        Territory == "Glorieuse Islands (France)" & Neighbour == "Mayotte (France)" |
        Neighbour == "Glorieuse Islands (France)" & Territory == "Mayotte (France)" |
        Territory == "Guam (USA)" & Neighbour == "Northern Marianas (USA)" |
        Neighbour == "Guam (USA)" & Territory == "Northern Marianas (USA)" |
        Territory == "Italy" & Neighbour == "Sardinia (Italy)" |
        Neighbour == "Italy" & Territory == "Sardinia (Italy)" |
        Territory == "Italy" & Neighbour == "Sicily (Italy)" |
        Neighbour == "Italy" & Territory == "Sicily (Italy)" |
        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (main islands)"|
        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (main islands)"|
        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (Ogasawara Islands)"|
        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (Ogasawara Islands)"|
        Territory == "Norway" & Neighbour == "Svalbard Isl. (Norway)" |
        Neighbour == "Norway" & Territory == "Svalbard Isl. (Norway)" |
        Territory == "Sicily (Italy)" & Neighbour == "Sardinia (Italy)" |
        Neighbour == "Sicily (Italy)" & Territory == "Sardinia (Italy)" |
        Territory == "South Africa (Atlantic Coast)" & Neighbour == "South Africa (Indian Ocean Coast)" |
        Neighbour == "South Africa (Atlantic Coast)" & Territory == "South Africa (Indian Ocean Coast)" |
        Territory == "USA (Alaska, Arctic)" & Neighbour == "USA (Alaska, Subarctic)" |
        Neighbour == "USA (Alaska, Arctic)" & Territory == "USA (Alaska, Subarctic)"
    ) %>%
    group_by(Territory,Neighbour) %>% 
    summarise(n())

  # Cleaned results 
  Clean_Results <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("Territory","Neighbour")
    ) %>% 
    filter(Same_Nation == "No") %>% 
    select(-8,-9)

  # Fix coding issues between MAC and Windows

  Clean_Results$Territory <- Clean_Results$Territory %>% 
    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
    gsub("R<e9>union (France)","Réunion",.)

  Clean_Results$Neighbour <- Clean_Results$Neighbour %>% 
    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
    gsub("R<e9>union (France)","Réunion",.)

  Clean_Results$CT_fishing_entity <- Clean_Results$CT_fishing_entity %>% 
    gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",.) %>% 
    gsub("C<f4>te d'Ivoire","Côte d'Ivoire",.) %>% 
    gsub("R<e9>union (France)","Réunion",.)

  return(Clean_Results)

@@

## Load Results data

# New dara produced by Vicky 
Clean_sau_eez_fes <- my_path("G","Spatial/SAU/","EEZ_FishingEntityID_v2_9June2020.xlsx", read =T)

# UN Regions dataset

@@

    sub_region = sub_region_name) %>% 

@@

# Load Land shapefile
World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
  st_transform(crs = "+proj=eck4") %>%
  # st_transform(crs = 4326) %>% # 4326
  rename(fishing_entity = name_long) %>% 
  mutate(
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    fishing_entity = gsub("Anguilla", "Anguilla (UK)",fishing_entity),
    fishing_entity = gsub("American Samoa (USA of America)", "American Samoa",fishing_entity),
    fishing_entity = gsub("Antigua & Barb.", "Antigua & Barbu",fishing_entity),
    fishing_entity = gsub("Aruba","Aruba (Netherlands)",fishing_entity),
    fishing_entity = gsub("Bermuda","Bermuda (UK)",fishing_entity),
    fishing_entity = gsub("Bonaire","Bonaire (Netherlands)",fishing_entity),
    fishing_entity = gsub("British Indian Ocean Territory","Brit. Indian Ocean Terr. (UK)",fishing_entity),
    fishing_entity = gsub("British Virgin Islands","British Virgin Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Cayman Islands","Cayman Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Christmas Island","Christmas Isl. (Australia)",fishing_entity),
    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    fishing_entity = gsub("Dem. Rep. Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Falkland Islands","Falkland Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Faeroe Islands","Faeroe Isl. (Denmark)",fishing_entity),
    fishing_entity = gsub("Federated States of Micronesia", "Micronesia",fishing_entity),
    fishing_entity = gsub("Guam","Guam (USA)",fishing_entity),
    fishing_entity = gsub("Northern Mariana Islands","North Marianas (USA)",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Marshall Isl.",fishing_entity),
    fishing_entity = gsub("Montserrat", "Montserrat (UK)",fishing_entity),
    fishing_entity = gsub("New Caledonia", "New Caledonia (France)",fishing_entity),
    fishing_entity = gsub("Niue", "Niue (New Zealand)",fishing_entity),
    fishing_entity = gsub("Norfolk Island", "Norfolk Isl. (Australia)",fishing_entity),
    fishing_entity = gsub("Pitcairn Islands","Pitcairn (UK)",fishing_entity),
    fishing_entity = gsub("Puerto Rico", "Puerto Rico (USA)",fishing_entity),
    fishing_entity = gsub("Republic of Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("Republic of Korea","Korea (South)",fishing_entity),
    fishing_entity = gsub("Saint Helena","Saint Helena (UK)",fishing_entity),
    fishing_entity = gsub("Saint-Martin","St Martin",fishing_entity),
    fishing_entity = gsub("Saint-Barthélemy","St Barthelemy (France)",fishing_entity),
    fishing_entity = gsub("Saint Pierre & Miquelon","Saint Pierre & Miquelon (France)",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Syria", "Syrian Arab Republic",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub("Turks & Caicos Islands", "Turks & Caicos Isl. (UK)",fishing_entity),
    fishing_entity = gsub("The Gambia","Gambia",fishing_entity),
    fishing_entity = gsub("United States", "USA",fishing_entity),
    fishing_entity = gsub("Vietnam", "Viet Nam",fishing_entity),
    fishing_entity = gsub("Wallis & Futuna Islands","Wallis & Futuna Isl. (France)",fishing_entity),
    fishing_entity = ifelse(fishing_entity == "USA Virgin Islands","US Virgin Isl.",fishing_entity)
  )

@@

# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
Entity_Area <- EEZ_Area %>% 
  left_join(Clean_sau_eez_fes,
            by = "eez_id") %>% 
  group_by(fishing_entity,fishing_entity_id) %>% 
  summarise(Size_Entity = sum(Size_EEZ))

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(eez_name=territory) %>% 
  mutate(
    eez_name = gsub("Brazil","Brazil (mainland)",eez_name),
    eez_name = gsub("Chile","Chile (mainland)",eez_name),
    eez_name = gsub("Curaçao","Curacao",eez_name),
    eez_name = gsub("Greenland","Greenland (Denmark)",eez_name),
    eez_name = gsub("United Kingdom","United Kingdom (UK)",eez_name),
    eez_name = gsub("US Virgin Islands","US Virgin Isl.",eez_name),
    eez_name = gsub("Vietnam","Viet Nam",eez_name),
    eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
                      ifelse(eez_name == "Spain", "Spain (mainland, Med and Gulf of Cadiz)",
                             ifelse(eez_name == "Greece","Greece (without Crete)",
                                    ifelse(eez_name == "Ecuador","Ecuador (mainland)",
                                           ifelse(eez_name == "Portugal","Portugal (mainland)",
                                                  ifelse(eez_name == "Italy","Italy (mainland)",
                                                         ifelse(eez_name =="Malaysia (Sarawak)","Sarawak",
                                                                ifelse(eez_name =="Saint Martin (France)","St Martin (France)",
                                                                       ifelse(eez_name =="South Africa (Atlantic Coast)","South Africa (Atlantic and Cape)",
                                                                              ifelse(eez_name =="Saba & Sint Eustaius (Netherlands)","Saba and Sint Eustaius (Netherlands)",
                                                                                     ifelse(eez_name =="Spain (Mediterranean and Gulf of Cadiz)","Spain (mainland, Med and Gulf of Cadiz)",
                                                                                            ifelse(eez_name =="Réunion (France)","Reunion (France)",
                                                                                                   eez_name)
                                                                                     )
                                                                              )
                                                                       )
                                                                )
                                                         )
                                                  )
                                           )
                                    )
                             )
                      )
    )
  )

# Load Transboundary Results

Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep ="")) %>% 
  mutate(
    eez_name = gsub("Brazil","Brazil (mainland)",eez_name),
    eez_name = gsub("Chile","Chile (mainland)",eez_name),
    eez_name = gsub("Greenland","Greenland (Denmark)",eez_name),
    eez_name = gsub("United Kingdom","United Kingdom (UK)",eez_name),
    eez_name = gsub("US Virgin Islands","US Virgin Isl.",eez_name),
    eez_name = gsub("Vietnam","Viet Nam",eez_name),
    eez_name = ifelse(eez_name == "Cote dIvoire","Côte d'Ivoire",
                      ifelse(eez_name == "Spain", "Spain (mainland, Med and Gulf of Cadiz)",
                             ifelse(eez_name == "Greece","Greece (without Crete)",
                                    ifelse(eez_name == "Ecuador","Ecuador (mainland)",
                                           ifelse(eez_name == "Portugal","Portugal (mainland)",
                                                  ifelse(eez_name == "Italy","Italy (mainland)",
                                                         ifelse(eez_name =="Malaysia (Sarawak)","Sarawak",
                                                                ifelse(eez_name =="Saint Martin (France)","St Martin (France)",
                                                                       ifelse(eez_name =="South Africa (Atlantic Coast)","South Africa (Atlantic and Cape)",
                                                                              ifelse(eez_name =="Saba & Sint Eustaius (Netherlands)","Saba and Sint Eustaius (Netherlands)",
                                                                                     eez_name)
                                                                       )
                                                                )
                                                         )
                                                  )
                                           )
                                    )
                             )
                      )
    )
    )

@@

Tresholded_T_Data <- Clean_Results_Trans %>% 
  filter(
    area_index >= Min_AI,
    area_index <= Max_AI,
    model_index >= MI
  ) %>% 
  select(-fishing_entity) %>% 
  left_join(Clean_sau_eez_fes, by = "eez_name")

@@

# Number of coastal territories
length(unique(sau_eez_fes$fishing_entity))

@@

Discrete <- Clean_Results_Trans %>% 
  filter(
    area_index < Min_AI |
      area_index > Max_AI |
      model_index < MI
  ) %>% 
  # Needed to correct for names
  select(-fishing_entity) %>% 
  left_join(Clean_sau_eez_fes,
            by = "eez_name") %>% 
  # Remove Countries that share with other countries
  anti_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity")
  )

@@

Value_Trans_Country <- Tresholded_T_Data %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,fishing_entity_id,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total, #million /1000000
                         ifelse(Variable == "catch",Trans_Total, #thousand Trans_Total/1000
                                Trans_Total)
    )
  ) %>%
  spread(Variable,Trans_Total) %>%
  left_join(Entity_Area, 
            by = c("fishing_entity","fishing_entity_id")
          # by = "fishing_entity"
  ) %>% 
  # Include the weighted method for supplementals
  mutate_at(
    vars(catch,value),
    funs(weight= ./Size_Entity) # back to USDs
  ) %>% 
  gather("Variable","Value",catch:value,catch_weight:value_weight) %>% 
  mutate(
    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
    Bins_Plot = cut(Value, breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_Entity,
            by = c("fishing_entity_id", "Variable") 
  ) %>%
  # Convert catch to million tonnes
  ungroup() %>% 
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                   Value),
    Trans_Per = (Value/Total_Value)#*100000000 #Return to percentage
  )

@@

Weighted_Data <- Subregion_Trans_Value %>% 
  mutate(
    Value_sum = ifelse(Variable == "value_weight", Value_sum/1000, Value_sum),
    Value_m = ifelse(Variable == "value_weight", Value_m/1000, Value_m),
    Value_sd = ifelse(Variable == "value_weight", Value_sd/1000, Value_sd)
    ) # Thousand) # Thousand) # Thousand

@@

# Old code
```{r OLD_funEstNeighbours, eval = F, echo=T}
# Determine which countries are Neighbours

>>>>

# Requires Clean_sau_eez_fes
# Data <- Results_Trans
CleanResults <- function(Data,names_data){

  clean_names_data <- names_data %>% 
    select(
      eez_id,
      fishing_entity_id,
      fishing_entity = sau_fishing_entity,
      eez_name = sf_eez_name
    )

  # Clean out countries that share with their own borders (e.g. Brazil mainland and Brazil (Fernando de Noronha))
  Auto_Remove_Territories <- Data %>% 
    filter(!is.na(territory),
           territory != "NA",
           !is.na(neighbour),
           neighbour != "NA") %>% 
    rename(eez_name=territory) %>% 
    left_join(clean_names_data,
              by = "eez_name") %>% 
    select(taxon_key,
           territory = eez_name,
           eez_name = neighbour, 
           model_index,
           area_index,
           ct_fishing_entity= fishing_entity) %>% 
    left_join(clean_names_data,
              by = "eez_name") %>% 
    select(1,2, 
           neighbour = eez_name,
           model_index:ct_fishing_entity,
           nt_fishing_entity= fishing_entity,
           everything()) %>% 
    mutate(
      ct_fishing_entity = ifelse(is.na(ct_fishing_entity),paste(territory),paste(ct_fishing_entity)),
      nt_fishing_entity = ifelse(is.na(nt_fishing_entity),paste(neighbour),paste(nt_fishing_entity)),
      Same_Nation = ifelse(ct_fishing_entity==nt_fishing_entity,"Yes","No")
    ) %>% 
    filter(neighbour != "NA")

@@

  # Complete list of territories to remove from dataset (Including islands)
  Territories_to_Remove <- Data %>% 
    filter(
      territory %in% Islands_to_Remove |
        neighbour %in% Islands_to_Remove |
        territory == "Balearic Island (Spain)" & neighbour == "Spain (Mediterranean and Gulf of Cadiz)" |
        territory == "British Virgin Isl. (UK)" & neighbour == "Anguilla" |
        neighbour == "British Virgin Isl. (UK)" & territory == "Anguilla" |
        territory == "Corsica (France)" & neighbour == "France (Mediterranean)" |
        neighbour == "Corsica (France)" & territory == "France (Mediterranean)" |
        territory == "Crete (Greece)" & neighbour == "Grece" |
        neighbour == "Crete (Greece)" & territory == "Grece" |
        territory == "Cyprus (North)" & neighbour == "Cyprus (South)" |
        neighbour == "Cyprus (North)" & territory == "Cyprus (South)" |
        territory == "Channel Isl. (UK)" & neighbour == "United Kingdom" |
        neighbour == "Channel Isl. (UK)" & territory == "United Kingdom" |
        territory == "Glorieuse Islands (France)" & neighbour == "Mayotte (France)" |
        neighbour == "Glorieuse Islands (France)" & territory == "Mayotte (France)" |
        territory == "Guam (USA)" & neighbour == "Northern Marianas (USA)" |
        neighbour == "Guam (USA)" & territory == "Northern Marianas (USA)" |
        territory == "Italy" & neighbour == "Sardinia (Italy)" |
        neighbour == "Italy" & territory == "Sardinia (Italy)" |
        territory == "Italy" & neighbour == "Sicily (Italy)" |
        neighbour == "Italy" & territory == "Sicily (Italy)" |
        territory == "Japan (Daito Islands)" & neighbour == "Japan (main islands)"|
        neighbour == "Japan (Daito Islands)" & territory == "Japan (main islands)"|
        territory == "Japan (Daito Islands)" & neighbour == "Japan (Ogasawara Islands)"|
        neighbour == "Japan (Daito Islands)" & territory == "Japan (Ogasawara Islands)"|
        territory == "Norway" & neighbour == "Svalbard Isl. (Norway)" |
        neighbour == "Norway" & territory == "Svalbard Isl. (Norway)" |
        territory == "Sicily (Italy)" & neighbour == "Sardinia (Italy)" |
        neighbour == "Sicily (Italy)" & territory == "Sardinia (Italy)" |
        territory == "South Africa (Atlantic Coast)" & neighbour == "South Africa (Indian Ocean Coast)" |
        neighbour == "South Africa (Atlantic Coast)" & territory == "South Africa (Indian Ocean Coast)" |
        territory == "USA (Alaska, Arctic)" & neighbour == "USA (Alaska, Subarctic)" |
        neighbour == "USA (Alaska, Arctic)" & territory == "USA (Alaska, Subarctic)"
    ) %>%
    group_by(territory,neighbour) %>% 
    summarise(n())

  # Cleaned results 
  Clean_Results <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("territory","neighbour")
    ) %>% 
    filter(Same_Nation == "No") %>% 
    select(taxon_key,
          eez_name = territory,
          eez_neighbour = neighbour,
          model_index,
          area_index
          )

  return(Clean_Results)
}

@@

### Standarization of names

```{standarize_names, eval = F, echo = F}

### --------------------- ###
# Sea Around Us eez to fishing entity
Clean_sau_eez_fes <- my_path("G","Spatial/SAU/","EEZ_FishingEntityID_v2_9June2020.xlsx", read =T)
### --------------------- ###

### --------------------- ###
# UNited Nations Dataset
### --------------------- ###

@@

    sub_region = sub_region_name,
    country_or_area) %>% 

@@

### --------------------- ###
# Natural Earth Shapefile
### --------------------- ###

World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
  st_transform(crs = "+proj=eck4") %>%
  # st_transform(crs = 4326) %>% # 4326
  rename(fishing_entity = name_long) %>% 
  mutate(
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    fishing_entity = gsub("Anguilla", "Anguilla (UK)",fishing_entity),
    fishing_entity = gsub("American Samoa (USA of America)", "American Samoa",fishing_entity),
    fishing_entity = gsub("Antigua & Barb.", "Antigua & Barbu",fishing_entity),
    fishing_entity = gsub("Aruba","Aruba (Netherlands)",fishing_entity),
    fishing_entity = gsub("Bermuda","Bermuda (UK)",fishing_entity),
    fishing_entity = gsub("Bonaire","Bonaire (Netherlands)",fishing_entity),
    fishing_entity = gsub("British Indian Ocean Territory","Brit. Indian Ocean Terr. (UK)",fishing_entity),
    fishing_entity = gsub("British Virgin Islands","British Virgin Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Cayman Islands","Cayman Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Christmas Island","Christmas Isl. (Australia)",fishing_entity),
    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    fishing_entity = gsub("Dem. Rep. Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Falkland Islands","Falkland Isl. (UK)",fishing_entity),
    fishing_entity = gsub("Faeroe Islands","Faeroe Isl. (Denmark)",fishing_entity),
    fishing_entity = gsub("Federated States of Micronesia", "Micronesia",fishing_entity),
    fishing_entity = gsub("Guam","Guam (USA)",fishing_entity),
    fishing_entity = gsub("Northern Mariana Islands","North Marianas (USA)",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Marshall Isl.",fishing_entity),
    fishing_entity = gsub("Montserrat", "Montserrat (UK)",fishing_entity),
    fishing_entity = gsub("New Caledonia", "New Caledonia (France)",fishing_entity),
    fishing_entity = gsub("Niue", "Niue (New Zealand)",fishing_entity),
    fishing_entity = gsub("Norfolk Island", "Norfolk Isl. (Australia)",fishing_entity),
    fishing_entity = gsub("Pitcairn Islands","Pitcairn (UK)",fishing_entity),
    fishing_entity = gsub("Puerto Rico", "Puerto Rico (USA)",fishing_entity),
    fishing_entity = gsub("Republic of Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("Republic of Korea","Korea (South)",fishing_entity),
    fishing_entity = gsub("Saint Helena","Saint Helena (UK)",fishing_entity),
    fishing_entity = gsub("Saint-Martin","St Martin",fishing_entity),
    fishing_entity = gsub("Saint-Barthélemy","St Barthelemy (France)",fishing_entity),
    fishing_entity = gsub("Saint Pierre & Miquelon","Saint Pierre & Miquelon (France)",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Syria", "Syrian Arab Republic",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub("Turks & Caicos Islands", "Turks & Caicos Isl. (UK)",fishing_entity),
    fishing_entity = gsub("The Gambia","Gambia",fishing_entity),
    fishing_entity = gsub("United States", "USA",fishing_entity),
    fishing_entity = gsub("Vietnam", "Viet Nam",fishing_entity),
    fishing_entity = gsub("Wallis & Futuna Islands","Wallis & Futuna Isl. (France)",fishing_entity),
    fishing_entity = ifelse(fishing_entity == "USA Virgin Islands","US Virgin Isl.",fishing_entity)
  ) %>% 
  as.data.frame() %>% 
  select(-geometry)

### --------------------- ###
# SAU Shapefile
### --------------------- ###
path_world <- paste(my_path("G"),"Spatial/SAU/SAU_Shapefile",sep="")

# Load it!
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(eez_name = Name,
         eez_id = EEZID) %>% 
  st_transform(crs = "+proj=eck4") %>% 
  mutate(
    eez_id = ifelse(eez_name == "Russia (Laptev to Chukchi Sea)",913,eez_id)
  ) %>% 
  clean_names()

World_df <- as.data.frame(World_sf) %>% 
  select(objectid, eez_id,eez_name)

World_sf %>% anti_join(Clean_sau_eez_fes, by = "eez_id")

# Join all tables with matching names

matching_names <- Clean_sau_eez_fes %>% 
  full_join(World_df,
            by = "eez_id") %>% 
  full_join(UN_Regions,
            by = "fishing_entity") %>% 
  full_join(World_land_sf,
            by = "fishing_entity") %>% 
  filter(!is.na(fishing_entity_id)) %>% # Remove duplicaates from UN_regions
  rename(sau_eez_name = eez_name.x,
         sau_fishing_entity = fishing_entity,
         sf_eez_name = eez_name.y,
         sf_object_id = objectid,
         un_country = country_or_area,
         un_geo_region = georegion,
         un_sub_region = sub_region
  ) %>% 
  select(
    eez_id,
    fishing_entity_id,
    sau_eez_name,
    sau_fishing_entity,
    sf_eez_name,
    sf_object_id,
    un_country,
    un_geo_region,
    un_sub_region,
    iso_a3
  )

# Save data for future
write_csv(matching_names,
          "matching_names.csv")

````
## Load Results data

# ----------------- #
# Misc.
# ----------------- #

# Dataset to match all SAU names
matching_names <- my_path("G"),"Spatial/SAU", "matching_names.csv", read = T)

# ----------------- #
# Data #
# ----------------- #

# Load Transbonudary results
Raw_Results_Trans <- my_path("R","EEZ","Raw_Results_Trans.xlsx", read = T)
Clean_Results_Trans <- Raw_Results_Trans %>% 
  CleanResults(.,clean_names) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(matching_names,
            by = "sf_eez_name") %>% 
  rename(eez_name = sf_eez_name,
         fishing_entity = sau_fishing_entity)

# New data produced by Vicky to compare with Teh and Sumaila
Clean_sau_eez_fes <- my_path("G","Spatial/SAU/","EEZ_FishingEntityID_v2_9June2020.xlsx", read =T)

# UN Regions dataset
UN_Regions <- read.csv(paste(my_path("D"),"Spatial/UN_Regions.csv",sep=""), header = TRUE) %>% 
  clean_names() %>% 
  group_by(
    un_country = country_or_area,
    georegion = region_name,
    sub_region = sub_region_name) %>% 
  summarise(n=n()) %>% 
  left_join(matching_names) %>% 
  ungroup() %>% 
  distinct(un_country,.keep_all = TRUE) %>% 
  select(fishing_entity = sau_fishing_entity,georegion,sub_region)

# Load Land shapefile
World_land_sf <- rnaturalearth::ne_countries(scale = 'medium', returnclass = c("sf")) %>% 
  st_transform(crs = "+proj=eck4") %>%
  # st_transform(crs = 4326) %>% # 4326
  left_join(matchig_names,
            by = "iso_a3") %>% 
  distinct(iso_a3,.keep_all = TRUE) %>% 
  rename(fishing_entity = sau_fishing_entity)

@@

# Entity Area (e.g. Mexico = Pacific EEZ + Atalntic EEZ)
Entity_Area <- EEZ_Area %>% 
  left_join(matchig_names,
            by = "eez_id") %>% 
  group_by(fishing_entity = sau_fishing_entity,fishing_entity_id) %>% 
  summarise(Size_Entity = sum(Size_EEZ))

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(sf_eez_name=territory) %>% 
  left_join(clean_names) %>% 
  rename(eez_name = sau_eez_name)
```

@@

Tresholded_T_Data <- Clean_Results_Trans %>% 
  filter(
    area_index >= Min_AI,
    area_index <= Max_AI,
    model_index >= MI
  )

@@

# Number of coastal territories
length(unique(Clean_sau_eez_fes$fishing_entity))

@@

Discrete <- Clean_Results_Trans %>% 
  filter(
    area_index < Min_AI |
      area_index > Max_AI |
      model_index < MI
  ) %>% 
  # Needed to correct for names
  # select(-fishing_entity) %>% 
  # left_join(Clean_sau_eez_fes,
            # by = "eez_name") %>% 
  # Remove Countries that share with other countries
  anti_join(Tresholded_T_Data,
            by = c("taxon_key","fishing_entity")
  )

@@

Value_Trans_Country <- Tresholded_T_Data %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Sampled_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity,fishing_entity_id,Variable) %>% # Estimate the amount of dollars of each nation 
  summarise(
    Trans_Entity_n = length(unique(taxon_key)),
    Trans_Total = sum(Value,na.rm=T), #million
  ) %>%
  ungroup() %>%
  filter(!is.na(Variable)) %>%
  mutate(
    Trans_Total = ifelse(Variable == "value",Trans_Total/1000000, #million /1000000
                         ifelse(Variable == "catch",Trans_Total/1000, #thousand Trans_Total/1000
                                Trans_Total)
    )
  ) %>%
  spread(Variable,Trans_Total) %>%
  left_join(Entity_Area, 
            by = c("fishing_entity","fishing_entity_id")
          # by = "fishing_entity"
  ) %>% 
  # Include the weighted method for supplementals
  mutate_at(
    vars(catch,value),
    funs(weight= ./Size_Entity) # back to USDs
  ) %>% 
  gather("Variable","Value",catch:value,catch_weight:value_weight) %>% 
  mutate(
    Bins = cut(Value, breaks = Map_Breaks, dig.lab = 5),
    Bins_Plot = cut(Value, breaks = Map_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  left_join(Total_Value_Entity,
            by = c("fishing_entity_id", "Variable") 
  ) %>%
  # Convert catch to million tonnes
  ungroup() %>% 
  mutate(
    Value = ifelse(Variable == "catch",Value/1000, #million
                   Value),
    Trans_Per = (Value/Total_Value*100000000)#*100000000 #Return to percentage
  )

@@

Weighted_Data <- Subregion_Trans_Value %>% 
  mutate(
    Value_sum = ifelse(Variable == "value_weight", Value_sum*1000, Value_sum),
    Value_m = ifelse(Variable == "value_weight", Value_m*1000, Value_m),
    Value_sd = ifelse(Variable == "value_weight", Value_sd*1000, Value_sd),
    Value_sum = ifelse(Variable == "catch_weight", Value_sum*1000, Value_sum),
    Value_m = ifelse(Variable == "catch_weight", Value_m*1000, Value_m),
    Value_sd = ifelse(Variable == "catch_weight", Value_sd*1000, Value_sd)
    )

@@

# Old code
